A Journey from Wild to Textbook Data to Reproducibly Refresh the Wages Data from the National Longitudinal Survey of Youth Database

### 2022-02-09 paper/paper.Rmd
Add explanation of how to obtain the work experience-reated variables.

Our target variables for the employment are to obtain respondent's mean hourly wage (`mean_hourly_wage`), the number of jobs (`number_of_jobs`) and the total hours of work per week (`total_hours`) for each survey year. As the data only reports up to 5 jobs for each respondent, the maximum number of jobs is capped at 5.

@@

>>>>

Our target variables for the employment are to obtain respondent's mean hourly wage (`wage`), the number of jobs (`njobs`), the total hours of work per week (`hours`) for each survey year, the year when individual starting to work (`stwork`), the length of time (years) in workforce (`yr_workforce`), and work experience measured as the number of years worked (`exp`). As the data only reports up to 5 jobs for each respondent, the maximum number of jobs is capped at 5.

@@

For `st_work` variable,  we only rename the column names from the raw, NLSY79 data. This variable is then used to calculate the next variable, `yr_workforce` for each survey round, which is the year of survey (`year`) minus the year of individual start working (`st_work`). Finally, `exp` variable is derived from the variable started with `WKSWK` in `new_data_qnames`. This variable measured since the last interview. Thus, to obtain the work experience since 1979, we calculate the cumulative value. As the measurement unit is in week, we convert this to year.
